### 2018-01-26 ApproxComp/sec-query.tex

Though lossless compression methods incur no information loss, their compression ratios are typically poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}. Hence, lossy techniques become the mainstream for trajectory compression,
which provide approximate solutions with good compression ratios and bounded errors.

Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a sub set of the former), such that the maximum distance of the former from the later is bounded by a user specified constant. It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

@@

An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing, and
the difficulty comes from the need to achieve effective compression ratios.
Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window. That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed. Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.

 We develop a  fitting function such that a data point is checked only once during the entire process of trajectory simplification. Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms that scan each data point in a trajectory once and only once. By comparing our algorithms with \fbqsa (\emph{the fastest} existing \lsa online algorithm \cite{Liu:BQS}) and \dpa (the {\em best} existing \lsa batch algorithm in terms of {\em compression ratio} \cite{Douglas:Peucker}), our one-pass algorithms are over four times faster than \fbqsa, and have  comparable compression ratios with \dpa.

>>>>

Though lossless compression methods incur no information loss, their compression ratios are typically poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}. Hence, lossy techniques become the mainstream for trajectory compression,
which provide approximate solutions with good compression ratios and bounded errors in practice.

Piece-wise line simplification (\lsa) comes from computational geometry, whose target is to approximate a given finer piece-wise linear curve by another coarser piece-wise linear curve ({normally} a subset of the former), such that the maximum distance of the former from the later is bounded by a user specified constant. It is widely used due to its distinct advantages: (a) simple and easy to implement, (b) no need of extra knowledge and suitable for freely  moving  objects, and (c) bounded errors with good compression ratios.

@@

An \lsa algorithm is {\em one-pass} if it processes each point in a trajectory once and only once when compressing the trajectory.
Obviously, one-pass algorithms have low time and space complexities, and are more appropriate for online processing. The difficulty comes from the need to achieve effective compression ratios.
Existing trajectory simplification algorithms (\eg \cite{Douglas:Peucker}) and online algorithms  (\eg \cite{Liu:BQS}) essentially employ a global distance checking approach to assuring error bounds, although online algorithms restrict the checking within a window. That is to say, whenever a new directed line segment is formed, these algorithms always check its distances to all or a subset of data points, and, therefore, a data point is checked multiple times, depending on its order in the trajectory and the number of directed line segments formed. Hence, {\em an appropriate local distance checking approach is needed in the first place for designing one-pass trajectory simplification algorithms}.

 We develop a  {\em fitting function} such that a data point is checked only once during the entire process of trajectory simplification. Based on the fitting function, we develop one-pass error bounded trajectory simplification algorithms \operb and \operba that scan each data point in a trajectory once and only once, allowing interpolating new data points or not, respectively. By comparing our algorithms with \fbqsa (the fastest existing \lsa online algorithm \cite{Liu:BQS}) and \dpa (the best existing \lsa batch algorithm in terms of compression ratio \cite{Douglas:Peucker}), our one-pass algorithms  \operb and \operba are over four times faster than \fbqsa, and have  comparable compression ratios with \dpa.
